### 2015-01-09 comparaison.tex
modif comparaison

\begin{figure}
\label{tab:reachability}
\noindent
\begin{tabular}{|l||c|c|c||c|c|c|c|c|}
  \hline
   Model& \#procs & \#states & target & Rocca & Pint & libddd & GINsim & ASP \\
  \hline
  tetard \cite{khalis2009smbionet} & 42 & $2^{19}$ & process & 7m17.01s & \todo{XX} & \todo{XX} & \todo{XX} & 0m01.90s \\
  \hline
  ERBB\_G1-S \cite{Samaga2009}  & 152 & $2^{70}$ & state & - & \todo{XX} &1m55.38s & 2m01.64s & 0m11.84s \\
  \hline
  ERBB\_G1-S & 152 & $2^{70}$ & process & - & 0m0.02s &1m54.96s & - & 0m05.02s \\
  \hline
  TCRsig40 \cite{Klamt06} & 156 & $2^{73}$ & process & - & \todo{XX} & out & out & 0m05.02s \\
  \hline
\end{tabular}
\caption{Compared performances of Rocca et al. method, \textsc{libddd}, \textsc{GINsim} and our new method developped in ASP. For each test we find the name of the model, the number of its processes and its states then the target(s). The target can be a network state (set of processes) or one or some processes. "out" marks an execution asking too much time or memory and "-" marks that is not possible to do the test.
}
\end{figure}
\end{center}
This table prensents the comparisons run for 4 dynamic analysis methods applied to examples of biological regulatory networks. The models of these networks where chosen as being representative of different scales, large networks and small networks.
This table shows the effectiveness of our method compared to existing. In fact we develop in the sequel that our method provides more compared to other

@@

\item[--] \textbf{PINT : }It should be noted that the only reachability analysis developed so far on the Process Hitting networks was implemented in the software Pint, and consists in an approximation: it is possible that it terminates but remains inconclusive (although this is rare). Moreover, it currently does not give us the path to activate the goal.
\end{itemize}

>>>>

\begin{figure}
\label{tab:reachability}
\noindent
\begin{tabular}{|l||c|c|c||c|c|c|c|c|}
  \hline
   Model& \#procs & \#states & target & Rocca & Pint & libddd & GINsim & ASP \\
  \hline
  tetard \cite{khalis2009smbionet} & 42 & $2^{19}$ & state & 7m17.01s & - & \todo{XX} & \todo{XX} & 0m01.90s \\
  \hline
  ERBB\_G1-S \cite{Samaga2009}  & 152 & $2^{70}$ & state & - & - &1m55.38s & 2m01.64s & 0m11.84s \\
  \hline
  ERBB\_G1-S & 152 & $2^{70}$ & process & - & 0m0.027s &1m54.96s & - & 0m05.02s \\
  \hline
  TCRsig40 \cite{Klamt06} & 156 & $2^{73}$ & process & - & 0m0.014s & out & - & 0m05.02s \\
  \hline
\end{tabular}
\caption{Compared performances of Rocca et al. method, \textsc{libddd}, \textsc{GINsim} and our new method developped in ASP. For each test we find the name of the model, the number of its processes and its states then the target(s). The target can be a network state (set of processes) or one or some processes. "out" marks an execution asking too much time or memory and "-" marks that is not possible to do the test.
}
\end{figure}
\end{center}
This table prensents the comparisons run for 4 dynamic analysis methods applied to examples of biological regulatory networks. The models of these networks where chosen as being representative of different scales, large networks and small networks.
This table shows the effectiveness of our method compared to existing. In fact we develop in the sequel that our method provides more compared to other

@@

\item[--] \textbf{PINT : }It should be noted that the only reachability analysis developed so far on the Process Hitting networks was implemented in the software Pint, and consists in an approximation: it is possible that it terminates but remains inconclusive (although this is rare). Moreover, it currently does not give us the path to activate the goal but only the "True" or "False" of the reachability. In the first example \textsc{PINT} did not give an answer because of the number of goals is greater than 5.
\end{itemize}
